\documentclass{article} % For LaTeX2e
\usepackage{iclr2025_conference,times}
\input{math_commands.tex}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{float}
\usepackage{multicol}
\usepackage{titlesec}

% --- Tighter spacing to fit two pages ---
\titlespacing*{\section}{0pt}{0.5ex plus 0.2ex minus 0.2ex}{0.3ex plus 0.1ex}
\titlespacing*{\paragraph}{0pt}{0.4ex plus 0.1ex minus 0.1ex}{0.5em}
\setlength{\textfloatsep}{2pt plus 1pt minus 1pt}
\setlength{\intextsep}{2pt plus 1pt minus 1pt}
\setlength{\abovedisplayskip}{3pt}
\setlength{\belowdisplayskip}{3pt}
\setlength{\abovedisplayshortskip}{1pt}
\setlength{\belowdisplayshortskip}{1pt}

% Use numeric [N] citations instead of author-year (shorter, less clutter)
\setcitestyle{numbers,square,comma}

\title{Forging Image Watermarks by Scheme Identification\\ and Native Re-encoding}

\author{%
\textbf{Muhammad Saad Haroon} \\
Matriculation No. 7088620 \\
Department of Computer Science \\
Universit\"at des Saarlandes \\
\texttt{muha00003@stud.uni-saarland.de}
\And
\textbf{Jayasankar Kumar Santhirani} \\
Matriculation No. 7089851 \\
Department of Computer Science \\
Universit\"at des Saarlandes \\
\texttt{jaku00013@stud.uni-saarland.de}
}

\newcommand{\bestscore}{0.8364}

\iclrfinalcopy

\begin{document}
\maketitle
\vspace{-1.6em}
\begin{center}
\small\textbf{Team V}\quad\textbullet\quad Code: \url{https://github.com/SaadH-077/TML-Watermark-Forging}
\end{center}
\vspace{-1.0em}

% -----------------------------------------------------------------------
\section{Introduction}
% -----------------------------------------------------------------------
We are given $8$ unknown image watermarking schemes $\mathrm{WM}_1,\dots,\mathrm{WM}_8$. For each scheme we
receive $25$ watermarked ``carrier'' images that all carry \emph{one} shared hidden message, and we must
transplant that watermark onto $25$ assigned clean target images so that a hidden detector recovers the
message while each forged image stays perceptually close to its target. The carriers and the targets are
different images, so this is true transplantation rather than re-stamping the same picture, and the
resolution is fixed per scheme. A submission is a flat archive of $200$ PNG files, one per target.

The score is $S_\text{final}=S_\text{det}\cdot S_\text{qlt}$, with
$S_\text{det}=\max\!\big(0,\,2(\text{bitacc}-0.5)\big)$ and $S_\text{qlt}=\exp(-8\,\text{LPIPS})$. Two
properties of this score decide the whole design. First, $S_\text{det}$ is a hard gate: a bit-accuracy of
$0.5$ sets $S_\text{det}=0$ and zeroes the image no matter how good it looks. Second, LPIPS is measurable
locally, but bit-accuracy is not, because we hold no detector. The only detection signal is the leaderboard,
which allows one submission per hour, keeps the best result, and scores on a $30\%$ public subset. The
practical consequence is that detection strength, not visual quality, is the binding constraint, so our rule
was to land the bits first and recover LPIPS second. Our final submission reaches a public score of
\textbf{\bestscore}.

% -----------------------------------------------------------------------
\section{Approach}
% -----------------------------------------------------------------------

\paragraph{Identification beats blind transplant.}
The averaging attack from the watermarking literature estimates the watermark as the mean carrier residual
and adds it to the target \citep{craver1998}. This fails on frequency-domain and content-adaptive marks. On
the first two schemes where we could also decode, the difference was clear: a native re-encode reached
$S_\text{final}=0.89$ (WM$_1$) and $0.86$ (WM$_2$), while an additive transplant scored close to $0$. The
better route is to \emph{identify} the scheme, decode the shared message from its carriers, and re-embed
that message into the target with the scheme's own genuine encoder. The forged image is then a real
watermark of that scheme, so it decodes at bit-accuracy $1.0$ and generalizes across the public and private
split. Identification became our main strategy.

\paragraph{The oracle test.}
Because the $25$ carriers share one message, we can identify a scheme without any detector. For a candidate
public decoder we decode all $25$ carriers: if they agree on a single message (carrier-agreement near $1.0$)
while clean images decode randomly (clean-agreement near $0.5$), the scheme is identified. We accepted a
match only with a \emph{validated positive control}, a genuine encode then decode round trip proving the
decoder reads real marks of that scheme, and a known-negative control from an already identified scheme.
This guarding mattered, because several apparent matches were artifacts. A common failure was a decoder that
returns a constant output regardless of its input; another was content correlation that also lifts clean
images. As one example, running classical decoders on WM$_3$'s chroma channels reports carrier-agreement
$1.000$, but the same decoder returns the identical constant bits on pure random noise, which is a
degenerate reading and not a recovered message.

\paragraph{What we did for each watermark.}
We identified seven of the eight schemes and re-encoded each one natively at round-trip bit-accuracy $1.0$
(Table~\ref{tab:schemes}). WM$_1$ is \texttt{dwtDct} from the \texttt{invisible-watermark} library, a
$30$-bit DWT-DCT mark whose message decodes as all ones; we re-embed with the genuine encoder and then
amplify the residual at strength $s=1.5$ to widen the quantization margin, which the robustness audit below
motivates. WM$_2$ is RivaGAN \citep{zhang2019riva}, a $32$-bit attention-based mark whose encoder sets the
quality floor among the natives at LPIPS $0.016$. WM$_4$ is VINE-R \citep{lu2025vine}, re-encoded with the
released generative-prior encoder at its native $256^2$. WM$_5$ is CIN \citep{ma2022cin} and WM$_6$ is MBRS
\citep{jia2021mbrs}, two learned encoder-decoder marks that we re-embed at their native $128^2$ and $256^2$.
WM$_7$ and WM$_8$ are two TrustMark variants \citep{bui2023trustmark} at $512^2$; WM$_8$ matched only after
we tried variant P with error correction disabled, which is why an earlier sweep of variant Q alone missed
it. WM$_3$ is the one scheme without a public decoder and is handled separately below.

\begin{table}[H]
\centering
\small
\caption{Per-scheme forge. The seven identified schemes are genuine native re-encodes (bit-accuracy $1.0$); WM$_3$ is the only transplant. LPIPS and $S_\text{final}$ are per-scheme local estimates.}
\label{tab:schemes}
\begin{tabular}{llll}
\toprule
WM & Scheme (message) & Forge & LPIPS / $S_\text{final}$ \\
\midrule
WM$_1$ & dwtDct, 30-bit                  & native re-encode, residual amplified $s{=}1.5$ & 0.006 / 0.89 \\
WM$_2$ & RivaGAN, 32-bit                 & native re-encode                                & 0.016 / 0.86 \\
WM$_3$ & custom chroma (unidentified)    & color-axis $R{+}B{-}2G$ transplant              & 0.023 / 0.43 \\
WM$_4$ & VINE-R, 100-bit                 & native re-encode ($256^2$)                      & 0.003 / 0.94 \\
WM$_5$ & CIN, 30-bit                     & native re-encode ($128^2$)                      & 0.001 / 0.99 \\
WM$_6$ & MBRS, 256-bit                   & native re-encode ($256^2$)                      & 0.002 / 0.96 \\
WM$_7$ & TrustMark-Q, 61-bit             & native re-encode ($512^2$)                      & 0.001 / 0.99 \\
WM$_8$ & TrustMark-P (no ECC), 100-bit   & native re-encode ($512^2$)                      & 0.001 / 0.99 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{WM$_3$: a custom scheme with no public decoder.}
For WM$_3$ we ruled out about $27$ public decoders under the positive-control bar, including all VINE
W-Bench baselines, RoSteALS, InvisMark, CRMark, Stable Signature \citep{fernandez2023}, LaWa, SepMark,
PIMoG, EditGuard, and classical and spread-spectrum families. From-scratch forensics place WM$_3$ in a
low-frequency, green-magenta chroma band that is content-adaptive and content-keyed. A Craver-style
diagnostic \citep{craver1998} makes the last point concrete: a norm-matched transplant of the averaged
template reaches bit-accuracy $0.88$ on the analogous VINE mark, near its optimum, but WM$_3$'s detector
accepts the same-quality template at only about $0.72$. So WM$_3$ has no public decoder to re-encode with,
and its per-image key limits any fixed-template transplant. Our best forge is a color-axis ($R{+}B{-}2G$)
chroma transplant with a bilateral-denoised template, capped near $S_\text{final}\approx0.43$. We confirmed
the ceiling three ways: a strength sweep plateaus, a robust estimator (a $20\%$ trimmed mean) that helps the
decodable analogs does not transfer to WM$_3$, and a learned diffusion forger stays below transplant parity,
held back by the $25$-carrier data limit.

\paragraph{Native robustness locates the residual gap.}
The leaderboard grades bit-accuracy after an unknown pre-detection transform, so clean-PNG bit-accuracy
overestimates the server. We built a local robustness oracle that decodes a forge, applies JPEG,
resizing, noise, and blur, then decodes again and measures the surviving bits. Six of the seven natives are
already robust and near optimal. Only WM$_1$, the classical dwtDct mark, is fragile, with surviving
bit-accuracy $0.60$ that collapses under JPEG. A leaderboard probe that strengthened WM$_1$'s quantization
margin was a wash of $+0.0002$: the quality cost cancelled the detection gain, and dwtDct is JPEG-fragile at
every strength. The natives therefore sit near their achievable ceiling under these public encoders, which
is an informative negative result rather than a missed lever.

% -----------------------------------------------------------------------
\section{Results}
% -----------------------------------------------------------------------
Table~\ref{tab:runs} shows the public leaderboard progression. Every gain came from a per-scheme method that
generalizes across the public and private split, not from tuning to the public sample. Identifying CIN and
MBRS added $0.057$; identifying VINE-R and TrustMark-P added another $0.10$; the two WM$_3$ steps and the
robustness work added the rest. Decomposing the total, the seven native schemes average about
$0.97\cdot S_\text{qlt}$ each while WM$_3$ contributes about $0.43$, so that single scheme is almost the
entire remaining gap to the strongest teams near $0.90$. The best submission rebuilds from the repository
with one command (\texttt{build\_best.py}), and every reported number has a script behind it.

\begin{table}[H]
\centering
\small
\caption{Public leaderboard score for each submitted configuration. Schemes are added and refined one change at a time so each step is attributable.}
\label{tab:runs}
\begin{tabular}{clc}
\toprule
Run & Configuration & Score \\
\midrule
1 & 3 native (WM$_1$, WM$_2$, WM$_7$) $+$ transplant elsewhere & 0.6613 \\
2 & $+$ CIN, MBRS native (5 native) & 0.7188 \\
3 & $+$ VINE-R, TrustMark-P native (7 native) $+$ WM$_3$ residual transplant & 0.8211 \\
4 & WM$_3$ in-band chroma transplant & 0.8268 \\
5 & $+$ perceptually-masked natives & 0.8274 \\
6 & WM$_3$ color-axis ($R{+}B{-}2G$) transplant & 0.8362 \\
\textbf{7} & \textbf{$+$ WM$_1$ residual amplification $s{=}1.5$} & \textbf{\bestscore} \\
\bottomrule
\end{tabular}
\end{table}

% -----------------------------------------------------------------------
\section{Conclusion}
% -----------------------------------------------------------------------
Watermark forgery under near black-box conditions is practical and cheap. For any deployed public scheme, an
attacker who collects a handful of same-message watermarked images can identify the scheme and re-encode
with its own public encoder, producing a genuine and generalizing forgery that stamps arbitrary content as
authentically watermarked and defeats provenance claims. Even unknown learned marks are partially forgeable
by averaging. The one scheme we could not forge to native quality, WM$_3$, is exactly the one that is
content-keyed with a non-public detector. That is the defensive lesson: reliable provenance needs secret,
content-bound, keyed watermarks whose detectors reject transplanted marks, not merely imperceptible marks
built on public or guessable encoders.

% -----------------------------------------------------------------------
% References
% -----------------------------------------------------------------------
\begingroup
\footnotesize
\setlength{\bibsep}{0pt}
\begin{multicols}{2}
\begin{thebibliography}{9}
\bibitem{craver1998}
S.~Craver, N.~Memon, B.-L.~Yeo, M.~M.~Yeung.
Resolving rightful ownerships with invisible watermarking techniques: limitations, attacks, and implications.
\textit{IEEE Journal on Selected Areas in Communications}, 1998.

\bibitem{zhang2019riva}
K.~A.~Zhang, L.~Xu, A.~Cuesta-Infante, K.~Veeramachaneni.
Robust invisible video watermarking with attention (RivaGAN).
\textit{arXiv:1909.01285}, 2019.

\bibitem{jia2021mbrs}
Z.~Jia, H.~Fang, W.~Zhang.
MBRS: enhancing robustness of DNN-based watermarking by mini-batch of real and simulated JPEG compression.
\textit{ACM Multimedia}, 2021.

\bibitem{ma2022cin}
R.~Ma, M.~Guo, Y.~Hou, F.~Yang, Y.~Li, H.~Jia, X.~Xie.
Towards blind watermarking: combining invertible and non-invertible mechanisms (CIN).
\textit{ACM Multimedia}, 2022.

\bibitem{fernandez2023}
P.~Fernandez, G.~Couairon, H.~J\'egou, M.~Douze, T.~Furon.
The stable signature: rooting watermarks in latent diffusion models.
\textit{ICCV}, 2023.

\bibitem{bui2023trustmark}
T.~Bui, S.~Agarwal, J.~Collomosse.
TrustMark: universal watermarking for arbitrary resolution images.
\textit{arXiv:2311.18297}, 2023.

\bibitem{lu2025vine}
S.~Lu, Z.~Zhou, J.~Lu, Y.~Zhu, A.~W.~K.~Kong.
Robust watermarking using generative priors against image editing (VINE).
\textit{ICLR}, 2025.
\end{thebibliography}
\end{multicols}
\endgroup

\end{document}
